EvoSuite at the SBST 2015 Tool Competition

### 2015-02-19 papers/sbst15/paper_sbst15.tex
adding EvoSuite description

  \hline
  \multicolumn{2}{|l|}{Operation} \\
  \hline
  Interaction &  Through the command line\\
  User guidance &  manual verification of assertions for functional faults\\
  Source of information &  http://www.evosuite.org \\
  Maturity&  Mature research prototype, under development\\
  Technology behind the tool & Search-based testing / whole test suite generation\\
\hline
  \multicolumn{2}{|l|}{Obtaining the tool and information} \\
  \hline
License & GNU General Public License V3\\
Cost & Open source\\
Support & None \\
\hline
\hline
  \multicolumn{2}{|l|}{Does there exist empirical evidence about} \\
  \hline
  Effectiveness and Scalability & See~\cite{GoA_TSE12,FrA12b}. \\
%Completeness & \\
%Effectiveness & \\
%Efficiency & \\
%Defect types & \\
%Scalability & \\
%Comprehensibility & \\
%Learnability & \\
%Subjective satisfaction & \\
%Other & \\
\hline
\end{tabular}\vspace{-1em}
\end{table}

>>>>

  \hline
  \multicolumn{2}{|l|}{Operation} \\
  \hline
  Interaction &  Through the command line, and Eclipse plugin\\
  User guidance &  manual verification of assertions for functional faults\\
  Source of information &  http://www.evosuite.org \\
  Maturity&  Mature research prototype, under development\\
  Technology behind the tool & Search-based testing / whole test suite generation\\
\hline
  \multicolumn{2}{|l|}{Obtaining the tool and information} \\
  \hline
License & GNU General Public License V3\\
Cost & Open source\\
Support & None \\
\hline
\hline
  \multicolumn{2}{|l|}{Does there exist empirical evidence about} \\
  \hline
  Effectiveness and Scalability & See~\cite{GoA_TSE12,fraser2014large}. \\
%Completeness & \\
%Effectiveness & \\
%Efficiency & \\
%Defect types & \\
%Scalability & \\
%Comprehensibility & \\
%Learnability & \\
%Subjective satisfaction & \\
%Other & \\
\hline
\end{tabular}\vspace{-1em}
\end{table}

\EVOSUITE~\cite{FrA11c,GoA_TSE12} automatically generates test suites
for Java classes, targeting branch coverage and other coverage
criteria (e.g., mutation testing~\cite{emse14_mutation}). \EVOSUITE
works at the Java bytecode level, i.e., it does not require source
code. It is fully automated and requires no manually written test
drivers or parameterized unit tests.  For example, when \EVOSUITE is
used from its Eclipse plugin, a user
just needs to select a class, and tests are generated with a mouse-click.

\EVOSUITE has been evaluated on millions of lines of Java code~\cite{fraser2014large}, both open-source
code and close-source code provided by one of our industrial partners. 
In the previous two editions
of the unit testing tool
competition, \EVOSUITE arrived first~\cite{evosuiteAtSbst2013,evosuiteAtFittest2013}.

\EVOSUITE uses an evolutionary approach to derive these test suites: A
genetic algorithm evolves candidate individuals (chromosomes) using
operators inspired by natural evolution (e.g., selection, crossover
and mutation), such that iteratively better solutions with respect to
the optimization target (e.g., branch coverage) are produced.  For
details on this test generation approach we refer to~\cite{GoA_TSE12}.
To improve performance further, we are investigating several
extensions to \EVOSUITE. 
For example, \EVOSUITE can employ dynamic
symbolic execution~\cite{evoISSRE113} 
and memetic algorithms~\cite{fraser2014memetic}
to handle the cases in which our genetic algorithm may struggle.

As the generated unit tests are meant for human consumption~\cite{fraser2013does}, \EVOSUITE
applies various post-processing steps to improve readability (e.g.,
minimising) and adds test assertions that capture the current
behavior of the tested classes. To select the most effective
assertions, \EVOSUITE uses mutation
analysis~\cite{10.1109/TSE.2011.93}. 
\EVOSUITE can also be used to automatically find faults in the CUTs~\cite{emse13_oracle}, e.g undeclared
thrown exceptions and broken code contracts.
 For more details on the tool and
its abilities we refer to~\cite{FrA11c}, and for more implementation
details we refer to~\cite{FrA13a}.
